Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-14 paper/draft1.tex

\begin{figure*}[!ht]
\centering
\includegraphics[width=.9\linewidth]{illustrator/fig_main_R1.pdf}
\caption{
XXX UPDATE THIS WITH (a) (b) (c) XXX
Computation speed for novel problem configurations using predictive
vs. empirical code specialization.
The scatterplots are roughly symmetric about the axis of equality (main diagonal)
with occasional outliers, indicating that for most problem configurations the
predictive approach gives as good a solution as the empirical approach.
The predictive approach typically requires about 0.1 seconds to suggest an
implementation, whereas the empirical approach requires about 2 minutes.
}
\label{fig:fig_gflop_scatter}
\end{figure*}

@@

Figure~\ref{XXX} shows how accurate predictive auto-tuning is compared with empirical auto-tuning.
The training set $(\mathcal{X}, \mathcal{Y})$ for the regression model comprised
all of the $<(a,b,c), y>$ pairs observed during grid search and hill-climbing search.
So for each training argument configuration $a,c$ there were 148 different values of $b$ and thus 148 training points.
Figure~\ref{XXX} shows that as more argument configurations are used for training,
the performance of predictive auto-tuning on test configurations $(a', c)$ quickly
approaches the average performance of empirical auto-tuning.
We took care to partition the train and test sets so that there were no overlapping configurations.
The key difference between the predictive and empirical auto-tuning,
is that predictive auto-tuning
typically took about 0.1 seconds per test example, whereas empirical auto-tuning took about 1-3 minutes.

@@

Figure~\ref{fig:speedup} also shows that random hill-climbing is at least
competitive and often better than the hand-chosen grid approach of ~\citet{pinto+cox:2011gcg}.  Figure~\ref{fig:hcX} shows how the number of hill-climbing iterations
affects the quality of the auto-tuned model.
The quicker HC25 approach is clearly inferior but the quality of the 75 iteration search (HC75) is statistically similar to the shorter HC50, suggesting that XXX.
Still, HC75 is not always better than the grid, so evidently neither search algorithm is perfect.

@@

\section{Conclusion}

Our

\bibliography{local}
\end{document}

>>>>

\begin{figure*}[!ht]
\centering
\includegraphics[width=.9\linewidth]{illustrator/fig_main_R1.pdf}
\caption{
Computation speed for novel problem configurations using predictive
vs. empirical auto-tuning.
(a) As more problem configurations are used to train the regression model,
the performance of predictive auto-tuning approaches that of empirical auto-tuning
despite taking only 0.1 seconds instead of 2 minutes.
(b) and (c) For a wide range of devices, implementation speeds found by predictive auto-tuning correlate tightly with
implementation speeds found by empirical auto-tuning.
%The boosted regression trees used for predictive auto-tuning generalize correctly across the implementation space.
}
\label{fig:fig_gflop_scatter}
\end{figure*}

@@

Figure~\ref{fig:fig_gflop_scatter} shows how accurate predictive auto-tuning is compared with empirical auto-tuning.
The training set $(\mathcal{X}, \mathcal{Y})$ for the regression model comprised
all of the $<(a,b,c), y>$ pairs observed during grid search and hill-climbing search.
So for each training argument configuration $a,c$ there were 148 different values of $b$ and thus 148 training points.
Figure~\ref{fig:fig_gflop_scatter} (a) shows that as more argument configurations are used for training,
the performance of predictive auto-tuning on test configurations $(a', c)$ quickly
approaches the average performance of empirical auto-tuning.
We took care to partition the train and test sets so that there were no overlapping configurations.
The key difference between the predictive and empirical auto-tuning,
is that predictive auto-tuning
typically took about 0.1 seconds per test example, whereas empirical auto-tuning took about 1-3 minutes.

Figure~\ref{fig:fig_gflop_scatter} (b) and (c) show that the implementation speeds found by predictive auto-tuning correlates very well with the speed of empirical auto-tuning across all of the devices we tested: GTX 580, GTX 480, GTX 296, Tesla C2070, and Tesla C1060 which span three generations of CUDA platforms.

@@

% DDC: XXX are these figures still in?
Figure~\ref{fig:speedup} also shows that random hill-climbing is at least
competitive and often better than the hand-chosen grid approach of ~\citet{pinto+cox:2011gcg}.  Figure~\ref{fig:hcX} shows how the number of hill-climbing iterations
affects the quality of the auto-tuned model.
The quicker HC25 approach is clearly inferior but the quality of the 75 iteration search (HC75) is statistically similar to the shorter HC50, suggesting that XXX.
Still, HC75 is not always better than the grid, so evidently neither search algorithm is perfect.

@@

% DDC: XXX is "Conclusion" a "required" section in any sense.  If not, I think we could probably do without
%\section{Conclusion}

%Our

{\small
    \bibliography{local}
}
\end{document}
